---
title: "Problem Set 4"
subtitle: Due Monday October 5 at 3PM
editor: 
  mode: source
---

> [Larry Wasserman](https://doi.org/10.1007/978-0-387-21736-9): "At a certain point in most probability courses, the sample space is rarely mentioned anymore and we work directly with random variables. But you should keep in mind that the sample space is really there, lurking in the background."




```{r}
#| echo: false
q_no <- 0
```

## Problem `{r} q_no`

{{< include bank/_music-rec.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

CONCEPTUAL

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/conditional-probability/dgs-exercise-2-3-1.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/conditional-probability/car-engine.qmd >}}


```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/bdj-rv.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/random-exam.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/gandalf-test.qmd >}}



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`


{{< include bank/random-variables-discrete/mak-rv.qmd >}}



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/binomial-lotus.qmd >}}



## Submission

{{< include bank/_submission.qmd >}}



