---
title: "Problem Set 4"
subtitle: Due Monday October 5 at 3PM
editor: 
  mode: source
---

> [Larry Wasserman](https://doi.org/10.1007/978-0-387-21736-9): "At a certain point in most probability courses, the sample space is rarely mentioned anymore and we work directly with random variables. But you should keep in mind that the sample space is really there, lurking in the background."




```{r}
#| echo: false
q_no <- 0
```

## Problem `{r} q_no`

{{< include bank/_music-rec.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/conceptual/perceptions.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/conditional-probability/dgs-exercise-2-3-1.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/conditional-probability/car-engine.qmd >}}


```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

::: callout-important
## Update (10/2/2026)
Skip part c.
:::

{{< include bank/random-variables-discrete/bdj-rv.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/random-exam.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/gandalf-test.qmd >}}



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/indicator-party.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`


{{< include bank/random-variables-discrete/mak-rv.qmd >}}



```{r}
#| echo: false
q_no <- q_no + 1
```

## Problem `{r} q_no`

{{< include bank/random-variables-discrete/binomial-lotus.qmd >}}

```{r}
#| echo: false
q_no <- q_no + 1
```

::: {.callout-tip collapse="true"}
## Hint

Before you launch into the calculation, spend some time staring at the right-hand side. Right now it may just look like a steaming pile of junk, but can the ingredients be interpreted *probabilistically*? What might $(n+1)p$ represent? What might $(1 - p)^{n+1}$ represent? What might $1 - (1 - p)^{n+1}$ represent? 
:::

## Problem `{r} q_no`

::: callout-important
## Update (10/2/2026)
Skip part c.
:::

{{< include bank/random-variables-discrete/zero-truncated-poisson.qmd >}}


## Submission

{{< include bank/_submission.qmd >}}



