---
title: "Typesetting math with LaTeX and Quarto"
format: html
editor: 
  mode: source
---

LaTeX is a software system for typesetting documents with a bunch of math in them[^1]. It is fully integrated into Quarto, so you can do all of your writing and coding and plotting and math-ing in one place. Pretty neat. We'll just show you a few things to get you going, but if you want to use the entire system for realz, you should make an [Overleaf](https://www.overleaf.com) account and [start playing](https://www.overleaf.com/learn).

[^1]: There is no consensus on how to pronounce "LaTeX." JZ says "*lah*-tech." Some folks say "*lay*-tech." Some even say "*lay*-techs," just like a latex glove. But we all agree that the emphasis is on the first syllable. Perhaps I'll award 2.56 bonus points if you invent a new way to pronounce it. But probably not.

## Inline math goes between single dollar signs

|  |  |
|----------------------------------------------------------|--------------|
| **Goal** | include an equation in the middle of a sentence |
| **What you type in the `.qmd` file** | `The function $h(x)=\ln x^2$ is my favorite` |
| **How it will look when you render** | The function $h(x)=\ln x^2$ is my favorite. |

: {tbl-colwidths="\[40,60\]"}

## A math block goes between double dollar signs

Say you want a whole bunch of math set off on a new line, in between your paragraphs, like this:

$$
f(x)=\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{1}{2}\frac{(x-\mu)^2}{\sigma^2}\right).
$$

In that case, you put this into your source `.qmd` file:

```{r}
#| eval: false
$$
f(x)=\frac{1}{\sqrt{2\pi\sigma^2}}\exp\left(-\frac{1}{2}\frac{(x-\mu)^2}{\sigma^2}\right).
$$
```

When you render, you'll get the pretty math. Notice some of the commands we used:

-   `\exp` for $\exp$;
-   `\sqrt{2}` for the square root $\sqrt{2}$;
-   `\frac{1}{2}` to get a fraction $\frac{1}{2}$;
-   `(x-\mu)^2` to get an exponent $(x-\mu)^2$;
-   `\mu`, `\sigma`, `\pi` for the Greek letters $\mu$, $\sigma$, and $\pi$;
-   and so on.

::: callout-tip
## Math commands in LaTeX

[Here](https://www.cmor-faculty.rice.edu/~heinken/latex/symbols.pdf) is a bank of common LaTeX commands. You won't use most of them. Alternatively, [Detexify](https://detexify.kirelabs.org/classify.html) is a very useful site where you can draw a symbol and it will tell you what the LaTeX command is for it.
:::

## Lining equations up

If you are typesetting a sequence of equalities, you should do it inside an `aligned` environment so that the equal signs are all lined up nice.

If you type this:

```{r}
#| eval: false
$$
\begin{aligned}
x(x+1)(x-1) &= (x^2+x)(x-1)\\
&=x^3-x^2+x^2-x\\
&=x^3-x.
\end{aligned}
$$
```

You will get this:

$$
\begin{aligned}
x(x+1)(x-1) &= (x^2+x)(x-1)\\
&=x^3-x^2+x^2-x\\
&=x^3-x.
\end{aligned}
$$

The `\\` introduces a line break, and the `&` in each equation tells it where to line things up.
