---
title: "Vectors"
format: html
editor: 
  mode: source
---

A **vector** in R is just an ordered set of values that have the same type. The easiest way to create one is to manually list out the values, separated by commas, inside `c()`:

```{r}
myvec <- c(pi, 5, 3.6, 2, 9, 6000) 
myvec
```

If you want to list out all of the integers between some min and max, you can use this shortcut:

```{r}
5:15
```

More generally, if you want a vector of evenly spaced numbers between a min and a max, do this:

```{r}
a <- seq(0, 1, length.out = 11) 
a
```

If you want to create a "blank" vector that just has zeros in it, here you go:

```{r}
z <- numeric(10)
z
```

In all of those cases, our vector contained numbers, but there is nothing special about numbers. Here is a vector where each value is a **string** (a piece of text):

```{r}
poetry <- c("Mary", "had", "a", "little", "chainsaw")
poetry
```

If you have two vectors and you want to combine them into one, you can just use the `c()` command again. The "c" stands for "concatenate." You're concatenating, or joining, the vectors end-to-end:

```{r}
more <- c("whose", "chain", "was", "red", "as")

masterpiece <- c(poetry, more)
masterpiece
```
